%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy-Edit - A fork of Deedy-Resume
% LaTeX Template
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% New authors:
% Gabriel Ong (http://q-gabe.me)
% Evan Tay (https://evantay.com)
%
% New repository:
% https://github.com/DigiPie/Deedy-Edit
%
% THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX not pdfLaTeX
%
% This template uses several fonts not included with Windows/Linux 
% by default. If you get compilation errors saying a font is missing, 
% find the line on which the font is used and either change it to a 
% font included with your operating system or comment the line out 
% to use the default font.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper]{deedy-resume-openfont} % For US Letter, change 'a4paper' to 'letterpaper'
\usepackage{fancyhdr}
\usepackage{tikz}
\usepackage[document]{ragged2e}
\pagestyle{fancy}
\fancyhf{}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Evan}{Tay}{Available from January 2021}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.34\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Contact} 
Email: \href{mailto:evan.it.sg@gmail.com}{\bf evan.it.sg@gmail.com} \\
Website: \href{https://www.evantay.com/}{\bf evantay.com} \\
Github: \href{https://github.com/DigiPie}{\bf github.com/DigiPie} \\
LinkedIn:  \href{https://www.linkedin.com/in/evanitsg/}{\bf linkedin.com/in/evanitsg/}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ABOUT ME 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{About me} 
Highly-motivated and independent problem-solver passionate about\\ solving meaningful challenges. Self-driven learner who thrives when working alongside cross-functional team members.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education} 
\subsection{National University \\ of Singapore}
\descript{B.Comp in Computer Science}
\location{August 2017 to December 2020}
cGPA: 4.14/5.00 (2nd Upper Honors)
\sectionsep
\subsection{Stanford University}
\descript{International Honors Program}
\location{June 2019 to August 2019}
One of only 10 NUS students selected for this prestigious summer quarter program.
\sectionsep
\subsection{Singapore Polytechnic}
\descript{Diploma with Merit in\\ Information Technology}
\location{April 2012 to March 2015}
GPA: 3.90/4.00 (Top 10\%)
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Certifications}
\location{AWS Certified Cloud Practitioner}
Issued on September 2020\\
\location{GCP Associate Cloud Engineer}
Issued on August 2020
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\location{Residential College 4 Systems Dynamics program}
Mapping connections with Network Sci.\\
Eating right(s): The Politics of Food\\
\location{Specialization in Networking}
Computer Networks Practice\\ 
Internet Architecture\\ 
\location{Specialization in Software Engineering}
Software Testing\\ 
Software Eng. Principles and Patterns\\ 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\location{Programming languages}
Fluent: Javascript and Java\\
Familiar: C, C++, C\# and Python\\
\location{Query languages}
MongoDB, PostgreSQL and MySQL \\
\location{Frameworks}
NodeJS, ExpressJS, ReactJS and VueJS
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\begin{minipage}[t]{0.60\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROFESSIONAL EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Professional Experience}
\runsubsection{National University of Singapore}\\
\location{Teaching Assistant | January 2018 to December 2020}
\vspace{10pt} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item {\fontsize{10}{10}\selectfont\bfseries Computer Networks Practice | August 2020 to December 2020}\\ Conducting weekly 2-hour labs for 16 students covering common network concepts such as SDN and IoT protocols such as MQTT.
\item {\fontsize{10}{10}\selectfont\bfseries Programming Methodology | August 2018 to December 2018}\\ Conducted weekly 2-hour tutorials on C and Vim for 14 students independently. View my {\bf \href{https://github.com/DigiPie/CS1010-Tutorial-C09}{teaching materials on Github}}.
\item {\fontsize{10}{10}\selectfont\bfseries Programming Methodology II | January 2018 to May 2018}\\ Produced lab materials on Java and OOP for over 200 students.
\end{tightemize}
\sectionsep

\runsubsection{Open Government Products}\\
\location{Software Engineering Intern | May 2020 to August 2020}
\begin{tightemize}
\item Contributed to Vault.gov.sg, a Whole-of-Government data discovery and sharing platform where public officers can access cross-agency data-sets for data-driven policy-making (i.e. {\bf \href{https://data.gov.sg/}{Data.gov.sg}} successor).
\item Worked as a Full-stack Software Engineer and Cloud Engineer in a cross-functional team. Collaborated with a Product Manager, a Product Designer and other Software Engineers on a daily basis.
\item {\fontsize{10}{10}\selectfont\bfseries Key Software Engineering achievement}: Rewrote and extended the data-set search feature, which is the primary way for all users to discover and access data-sets. Created a much more useful, accessible and accurate search experience.
\item {\fontsize{10}{10}\selectfont\bfseries Key Software Testing achievement}: Discovered a vulnerability which exposed confidential data-sets while writing integration tests, and patched it independently afterwards.
\item {\fontsize{10}{10}\selectfont\bfseries Key Cloud Engineering achievement}: Set up alarms for the AWS Elastic Beanstalk environment using Cloudwatch and Pub/Sub.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     OTHER EXPERIENCES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Activities \& Volunteering}
\runsubsection{NUS Google Developer Student Club}\\
\location{Deputy Head of Technology | November 2019 to June 2020}
\begin{tightemize}
\item Co-lead a team of 8 Tech Associates in organizing 6 workshops.
\item Co-organized and emceed for the first-ever Hack for Good hackathon, a Grab-sponsored event in which 28 teams participated.
\end{tightemize}
\sectionsep

\runsubsection{NUS Skating Club}\\
\location{President | September 2018 to September 2019}
\begin{tightemize}
\item Organized Skate Challenge 2019 in which over 60 university, polytechnic, ITE and primary school students participated.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Project Showcase}
\runsubsection{Dynalite}
\descript{Full-stack IoT Cloud-enabled web app}
\location{R-Pi • Python • COAP • ExpressJS • PostgreSQL • ReactJS • Docker}
\begin{tightemize}
\item Worked on Dynalite, an Internet-of-Things application which performs dynamic visualization of room occupancy.
\item Implemented the COAP-HTTP hybrid backend server which reads and stores COAP messages from the Raspberry-Pi in the database, and which also provides a HTTP REST API used by the frontend server to access the readings stored in the database.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{rll}
2019 & NUS Sports Club Colours Award for Outstanding Contributions\\
2018 & NUS School of Computing's Orbital Honorable Mention (Top 11/211)\\
2013 & First runner-up for Isobar Create32 Hackathon SG\\
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     OTHER EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% \section{Other Experience}
% \runsubsection{Armed Forces}
% \descript{| Webmaster}
% \location{Oct 2010 – Aug 2012 | }
% \begin{tightemize}
% \item Appointed as the Webmaster of the Medical Service.
% \item Implemented additional UI features onto an intranet website to improve user experience, utilising HTML5 and CSS knowledge.
% \item Involved in content maintenance and debugging of the website.
% \end{tightemize}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%\section{Research}
%\runsubsection{Cornell Robot Learning Lab}
%\descript{| Researcher}
%\location{Jan 2014 – Jan 2015 | Ithaca, NY}
%Worked with \textbf{\href{http://www.cs.cornell.edu/~ashesh/}{Ashesh Jain}} and \textbf{\href{http://www.cs.cornell.edu/~asaxena/}{Prof Ashutosh Saxena}} to create \textbf{PlanIt}, a tool which  learns from large scale user preference feedback to plan robot trajectories in human environments.  
%\sectionsep
%
%\runsubsection{Cornell Phonetics Lab}
%\descript{| Head Undergraduate Researcher}
%\location{Mar 2012 – May 2013 | Ithaca, NY}
%Led the development of \textbf{QuickTongue}, the first ever breakthrough tongue-controlled game with \textbf{\href{http://conf.ling.cornell.edu/~tilsen/}{Prof Sam Tilsen}} to aid in Linguistics research. 
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%\section{Publications} 
%\renewcommand\refname{\vskip -1.5cm} % Couldn't get this working from the .cls file
%\bibliographystyle{abbrv}
%\bibliography{publications}
%\nocite{*}
%

\end{minipage} 
\end{document}  \documentclass[]{article}
